---
title: "Descriptive Statistics & EpiAnalyses Report"
author: "Dewi Anastasia Christina"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

if(!require(pacman)) install.packages("pacman")
pacman::p_load(reactable, tidyverse, plotly)

```

## 1. Descriptive statistics

### 1.1. Methods

xxx

We calculated pneumococcal carriage prevalence among children by study site (Gunungkidul and Southwest Sumba), age group (\<1 year, 1–2 years, 3–4 years), and other factors potentially associated with pneumococcal colonization. The vaccine serotypes were those included in PCV13 (1, 3, 4, 5, 6A, 6B, 7F, 9V, 14, 18C, 19A, 19F, and 23F). S. pneumoniae isolates were deemed to be non-typeable if a serotype could not be determined by cmPCR and Quellung but showed positive results for lytA gene.

### 1.2. Results

#### 1.2.1. EpiData

The consensus based on selected variables to final_pneumo_decision = positive/negative

```{r}
# xxx

```

#### 1.2.2. Genome data

Filter out the data:

From positive samples, how many data failed to be processed due to RNA contaminations, etc.

Subset the data to only WGS-processed samples:

MLST, pneumoKITy and contamination profiles.

vaccine-types and non-vaccine-types

## 2. Epidemiological modelling and analyses

### 2.1. Methods

This

We used logistic regression models to obtain crude odds ratios (ORs) and adjusted ORs (adjusted by study site) to evaluate factors associated with pneumococcal carriage prevalence. We applied a multivariable logistic regression model to evaluate factors independently associated with pneumococcal carriage; a stepwise backwards elimination process was applied to the full model including all covariates, and variables were removed from the model when 0.05 significance level was not met. Data analyses were performed using Stata (version 15.0) and SAS (version 9.4) software. P values \<0.05 were considered statistically significant.

### 2.2. Results

#### 2.2.1. EpiData

sssss

Justifications for selecting multivariable logistic regression with backwise step.

No statistically significant results occured among variables.

#### 2.2.2. Genome data

ssssss

Multivariate analyses for serotype related to carriage, vaccine types and non-vaccine types,

## 3. Discussion and conclusion
