---
title: "Descriptive Statistics & EpiAnalyses Report"
author: "Dewi Anastasia Christina"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

if(!require(pacman)) install.packages("pacman")
pacman::p_load(reactable, tidyverse, plotly)

```

## 1. Descriptive statistics

This

### 1.1. EpiData

The consensus based on selected variables to final_pneumo_decision = positive/negative

```{r}
# xxx

```

### 1.2. Genome data

Filter out the data:

From positive samples, how many data failed to be processed due to RNA contaminations, etc.

Subset the data to only WGS-processed samples:

MLST, pneumoKITy and contamination profiles.

vaccine-types and non-vaccine-types

## 2. Epidemiological modelling and analyses

This

### 2.1. EpiData

sssss

Justifications for selecting multivariable logistic regression with backwise step.

No statistically significant results occured among variables.

### 2.2. Genome data

ssssss

Multivariate analyses for serotype related to carriage, vaccine types and non-vaccine types,

## Discussion and conclusion
